---
title: "If there's a 2nd UK lockdown, when will it be?"
author: "Andi (almost@gmail.com, @[inductivestep](https://twitter.com/InductiveStep))"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    self_contained: no
    toc: yes
    toc_float: yes
---

On 14th Sept 2020 I [asked](https://twitter.com/InductiveStep/status/1305447174201921537) Twitter, "When do you think Lockdown II is happening in the UK?"

Here are the results.

### Load packages

```{r message=FALSE}
library(tidyverse)
library(kableExtra)
```

And a helper:

```{r}
pretty_date <- function(d) format(d, format="%d %B %Y")
```


### Read and sort out the data

Load in the data:

```{r dat}
dat <- read.csv("guess_lockdown_2.csv")
```

It's just a single column: a list of all the guesses:

```{r}
head(dat)
```

Let's parse that as a date:

```{r guess_date}
dat$guess_date <- parse_date(dat$Date, format = "%d %B %Y")
head(dat)
```

### Take a look

The mean guess was `r pretty_date(mean(dat$guess_date))`.

The median was `r pretty_date(median(dat$guess_date))`.

Here's the frequency of the dates:

```{r guess_table}
guess_table <- dat %>%
  group_by(guess_date) %>%
  summarise(n = n())
```

Now a histogram of guesses, first with a binwidth of 1.

```{r fig.height=4, fig.width=8}
ggplot(dat, aes(x = guess_date)) +
  geom_histogram(binwidth=1) +
  xlab("Month") +
  ylab("Count")
```



```{r fig.height=4, fig.width=8}
ggplot(dat, aes(x = guess_date)) +
  geom_histogram(binwidth=4) +
  xlab("Month") +
  ylab("Count") + 
  scale_y_continuous(breaks=seq(0,10,1))
```



```{r}
mode_n <- max(guess_table$n)

mode_guesses <- guess_table %>%
  filter(n == mode_n)
```


The most common guess was `r pretty_date(mode_guesses$guess_date)`. 

The top 5 guesses were:

```{r}
guess_table %>%
  arrange(desc(n)) %>%
  top_n(5) %>%
  kbl() %>%
  kable_paper("hover", full_width = F)
```

Finally, here's a summary...

```{r}
summary(dat$guess_date)
```




